Supplemental Information B: Full Annotated Analysis and Reproducible Code

### 2021-10-03 Supplemental-Material-B-Annotated-Analysis.Rmd
Updates from Overleaf

---
title: "Supplemental Information B: Full Annotated Analysis and Reproducible Code"
subtitle: "Suppplemental Material for 'Psychological Needs During Intergroup Contact [working title]'"
author:
- Jannis Kreienkamp^1,2^
- Maximilian Agostini^1,2^
- Laura Bringmann^1,2^
- Peter de Jonge^1,2^
- Kai Epstude^1,2^
- ^1^University of Groningen
- ^2^Author order to be discussed currently alphabetic by last name
- "Author Information:"
- "Correspondence concerning this article should be addressed to Jannis Kreienkamp, Department of Psychology, University of Groningen, Grote Kruisstraat 2/1, 9712 TS Groningen (The Netherlands).  E-mail: <a href='mailto:j.kreienkamp@rug.nl'>j.kreienkamp@rug.nl</a>"
- 'The main manuscript is available at <a href="https://www.doi.org/ToBePublished" target="_blank">doi.org/ToBePublished</a>'
- 'The data repository for this manuscript is available at <a href="https://osf.io" target="_blank">OSF link goes here</a>'
- 'The GitHub repository for this manuscript is available at <a href="https://janniscodes.github.io/intergroup-contact-needs/" target="_blank">janniscodes.github.io/intergroup-contact-needs/</a>'
date: "Last updated: `r format(Sys.time(), '%d %B, %Y')`"
output: 
  bookdown::html_document2:
    fig_caption: yes
    md_extensions: +footnotes
    code_folding: hide
    mathjax: default
    theme: yeti
    toc: yes
    toc_float: yes
    number_sections: false
    css: style.css
    includes:
      in_header: "_includes/head-custom-rmd.html" 
editor_options:
  chunk_output_type: console
bibliography: references.bib
csl: apa.csl
---

>>>>

---
title: "Supplemental Information B: Full Annotated Analysis and Reproducible Code"
subtitle: "Suppplemental Material for 'Psychological Needs During Intergroup Contact [working title]'"
author:
- Jannis Kreienkamp^1,2^
- Maximilian Agostini^1,2^
- Laura Bringmann^1,2^
- Peter de Jonge^1,2^
- Kai Epstude^1,2^
- ^1^University of Groningen, Department of Psychology
- ^2^Author order to be discussed currently alphabetic by last name
- "Author Information:"
- "Correspondence concerning this article should be addressed to Jannis Kreienkamp, Department of Psychology, University of Groningen, Grote Kruisstraat 2/1, 9712 TS Groningen (The Netherlands).  E-mail: <a href='mailto:j.kreienkamp@rug.nl'>j.kreienkamp@rug.nl</a>"
- 'The main manuscript is available at <a href="https://www.doi.org/ToBePublished" target="_blank">doi.org/ToBePublished</a>'
- 'The data repository for this manuscript is available at <a href="https://osf.io" target="_blank">OSF link goes here</a>'
- 'The GitHub repository for this manuscript is available at <a href="https://janniscodes.github.io/intergroup-contact-needs/" target="_blank">janniscodes.github.io/intergroup-contact-needs/</a>'
date: "Last updated: `r format(Sys.time(), '%d %B, %Y')`"
output: 
  bookdown::html_document2:
    fig_caption: yes
    md_extensions: +footnotes
    code_folding: hide
    mathjax: default
    theme: yeti
    toc: yes
    toc_float: yes
    number_sections: false
    css: style.css
    includes:
      in_header: "_includes/head-custom-rmd.html" 
editor_options:
  chunk_output_type: console
bibliography: references.bib
csl: apa.csl
---
